---
title: "Doing Data Science - section 403 - Case Study 1"
author: "AFrancomano"
date: "June 19, 2018"
output: 
  html_document:
    keep_md: true
---

## Introduction
Steeped in a tradition of innovation for the past 150 years, the family-owned De Halve Maan brewery in Bruges, Belgium, is keen to expand its presence into the U.S. market.  Our team is assisting management with determining if there is a particular U.S. location (e.g. state or region) that would present an opportunity.  

Phase One of the analysis process assesses the geographical locations and products of the established U.S. breweries.


.. characteristics of its own products, general and specific measures, i.e. ABV ..   differentiate from those already offered by the U.S. breweries.

... 


## Question 1: Brewery Count by State

As part of evaluating geographic locations, Halv de Maan needs to know at a minimum how many U.S. breweries there are by state. 
...Include graphics here..
...Add data summarize by region ..  west, central, south, northeast


```{r echo=TRUE}
#a. Bring Breweries.txt into R   
USbrews <- read.csv("breweries.csv", header = TRUE)          #Read in the breweries datafile
dim(USbrews)                                               #confirm all data lines were read in

#b. Retrieve the last ten rows of the USbrews dataframe
tail(USbrews, 10)

#c.
#Verify that there are no NAs in each dataset before running analysis
sum(is.na(USbrews$Brew_ID))
sum(is.na(USbrews$Name))
sum(is.na(USbrews$City))
sum(is.na(USbrews$State))


# Count by State
USbrewsByState <- table(USbrews$State)
USbrewsByState
dim(USbrewsByState)

#barchart
par(las=2)
barplot(USbrewsByState, main = "Brewery Count by US State", xlab="Count", ylab="State", col="lightseagreen", horiz=TRUE)

#what are the top 10 states with the most number of breweries 
#SortDescByCount <- final[order(-final$Total),]   
#SortDescByCount[1:10, "State",] 


#Add Region column to the dataframe
USbrews$Region<-NA

#USbrews$Region[USbrews$State == 'MA'] <- "NE"  

NorthEastVector <- c("ME","NH","VT","MA", "CT", "RI","NY","NJ", "PA", "DE")
SouthVector <- c("MD","DC", "VA","NC","SC","GA","FL","TN","KY","AL","MS","LA","AR")
CentralVector <- c("TX","OK","KS","")
WestVector <- c("CA","WA")

USbrews$Region [is.element(USbrews$State, NorthEastVector)]  <- "NE" 



# Will we need to merge these files according to Brewery_ID field ....
#final <- merge (y2015, y2016, by=c("FirstName","Gender"))
                
```


## Question 5: Beer ABV Measure - Summary Statistics
```{r echo=TRUE}
##a. Bring Beers.csv into R   
USbeers <- read.csv("beers.csv", header = TRUE)          #Read in the beers datafile
dim(USbeers)

#b. 
summary(USbeers$ABV)
                
```

## Analysis Conclusion

conclusion here...

Suggested next steps for analysis.. take into consideration population to possible support another brewery in the potential areas of interest..

## Reference information, GitHub links, etc.

***THE GITHUB LINK IS  https://github.com/afrancomano/MSDSHomeWork5

